Estimating Correspondences of Deformable Objects ``In-the-wild"

### 2015-11-05 contents/evaluation.tex
Updates from ShareLaTeX

@@

\subsection{Benchmark Against State-of-the-art}
\label{exp:benchmark}
This experiment presented the accuracy of predicting joints positions from establishing dense correspondences with outline fitting. We build Patch AAM using 891 training hand images from a combination of datasets, where each image has 29 landmarks annotated alone its boundary. Dense scale-invariant feature transform (DSIFT)\cite{PoseletsICCV09} feature is used from image representation for our model. Model fitting is initialised based on current state-of-the-art human pose estimation algorithms on BBC Pose dataset. Results for this experiment are reported over 1000 testing images BBC Pose Provided, which human upper-body pose are landmark with 7 points on skeleton. For our model, joints are projected from the dense correspondence generated from our proposed method.

@@

\begin{table}[b!]
    \small
    \centering
    \begin{tabular}{|l|c|c|c||c|c|c|}
        \hline
                            & \multicolumn{3}{c||}{Wrist} & \multicolumn{3}{c|}{Elbow}\\
        \hline
        \emph{Method}       & \emph{mean} & \emph{std} & $\leq 6pt$ & \emph{mean} & \emph{std} & $\leq 6pt$\\
        \hline\hline
        Buehler             & 12.08    & 19.94        & 44.5\%       & 12.94    & 14.65        & 34.4\%\\
        Charles14           & 11.81    & 20.89        & 54.2\%       &  8.30    & 11.00        & \textbf{55.2\%}\\
        Charles13           & 13.78    & 22.39        & 43.3\%       & 13.17    & 18.74        & 46.3\%\\
        Pfister14           & 14.69    & 17.89        & 29.7\%       & 14.60    & 10.59        & 14.0\%\\
        Ramanan             & 15.59    & 19.04        & 22.6\%       & 15.53    & 10.82        & 15.8\%\\
        Pfister15           & 7.62     & 11.04        & 54.1\%       &  8.84    & 11.44        & 54.9\%\\
        \hline\hline
        Ours                & \textbf{6.791}& \textbf{10.910}   & \textbf{63.1\%}       & \textbf{8.250}     &  \textbf{10.564}        & 52.1\%\\
        \hline
    \end{tabular}
    \caption{Fitting statistics on BBC Pose database for experiment \ref{exp:benchmark}}
    \label{tab:hand_benchmark}
\end{table}

>>>>

\begin{figure}[t!]
    \centering
    \begin{subfigure}[b]{0.05\textwidth}
            \includegraphics[width=\textwidth]{resources/Fig_Variance/image_0}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.05\textwidth}
            \includegraphics[width=\textwidth]{resources/Fig_Variance/image_1}
    \end{subfigure}
  	\hfill
    \begin{subfigure}[b]{0.05\textwidth}
            \includegraphics[width=\textwidth]{resources/Fig_Variance/image_2}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.05\textwidth}
            \includegraphics[width=\textwidth]{resources/Fig_Variance/image_3}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.05\textwidth}
            \includegraphics[width=\textwidth]{resources/Fig_Variance/image_4}
    \end{subfigure}
  	\hfill
    \begin{subfigure}[b]{0.05\textwidth}
            \includegraphics[width=\textwidth]{resources/Fig_Variance/image_5}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.05\textwidth}
            \includegraphics[width=\textwidth]{resources/Fig_Variance/image_6}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.08\textwidth}
            \includegraphics[width=\textwidth]{resources/Fig_Variance/variances}
    \end{subfigure}
    \caption{Exemplar human pose annotation for left arm among four annotators. Large variance shows the difficulties of have consistent landmarks. Figure best viewed by zooming in.}
    \label{fig:variance}
\end{figure}

@@

\subsection{Benchmark Against State-of-the-art}
\label{exp:benchmark}
This experiment presented the accuracy of predicting joints positions from establishing dense correspondences with outline fitting. We build Patch AAM using 891 training hand images from a combination of datasets, where each image has 29 landmarks annotated alone its boundary. Dense Scale-Invariant Feature Transform (SIFT)\cite{PoseletsICCV09} feature is used from image representation for our model. Model fitting is initialised based on current state-of-the-art human pose estimation algorithms on BBC Pose dataset. Results for this experiment are reported over 1000 testing images BBC Pose Provided, which human upper-body pose are landmark with 7 points on skeleton. For our model, joints are projected from the dense correspondence generated from our proposed method.

@@

\begin{table}[b!]
    \small
    \centering
    \begin{tabular}{|l|c|c|c||c|c|c|}
        \hline
                            & \multicolumn{3}{c||}{Wrist} & \multicolumn{3}{c|}{Elbow}\\
        \hline
        \emph{Method}       & \emph{mean} & \emph{std} & $\leq 6pt$ & \emph{mean} & \emph{std} & $\leq 6pt$\\
        \hline\hline
        Buehler             & 12.08    & 19.94        & 44.5\%       & 12.94    & 14.65        & 34.4\%\\
        Charles14           & 11.81    & 20.89        & 54.2\%       &  8.30    & 11.00        & \textbf{55.2\%}\\
        Charles13           & 13.78    & 22.39        & 43.3\%       & 13.17    & 18.74        & 46.3\%\\
        Pfister14           & 14.69    & 17.89        & 29.7\%       & 14.60    & 10.59        & 14.0\%\\
        Ramanan             & 15.59    & 19.04        & 22.6\%       & 15.53    & 10.82        & 15.8\%\\
        Pfister15           & 7.62     & 11.04        & 54.1\%       &  8.84    & 11.44        & 54.9\%\\
        \hline\hline
        Ours                & \textbf{6.71}& \textbf{10.90}   & \textbf{63.1\%}       & \textbf{8.20}     &  \textbf{10.54}        & 52.1\%\\
        \hline
    \end{tabular}
    \caption{Fitting statistics on BBC Pose database for experiment \ref{exp:benchmark}}
    \label{tab:hand_benchmark}
\end{table}

### 2015-11-05 contents/introduction.tex

\begin{figure}[t!]
    \centering
    \begin{subfigure}[b]{0.09125\textwidth}
            \includegraphics[height=3.25cm]{resources/MotivativeAnnotation/MPII}
            \caption{MPII}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.1125\textwidth}
            \includegraphics[height=3.25cm]{resources/MotivativeAnnotation/FashionPose}
            \caption{Fashion}
    \end{subfigure}
  	\hfill
    \begin{subfigure}[b]{0.125\textwidth}
            \includegraphics[height=3.25cm]{resources/MotivativeAnnotation/FLIC}
            \caption{FLIC}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.125\textwidth}
            \includegraphics[height=3.25cm]{resources/MotivativeAnnotation/BBCPose}
            \caption{BBC Pose}
    \end{subfigure}
    \caption{Visualisation of inconsistent and inaccurate annotations of human pose among different datasets. Original annotation are shown in yellow dots while better annotations shown in blue dots.}
    \label{fig:wrong_anno}
\end{figure}
\begin{figure}[t!]
    \centering
    \begin{subfigure}[b]{0.065\textwidth}
            \includegraphics[height=2.55cm]{resources/Fig_Intro/intro_2_0}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.065\textwidth}
            \includegraphics[height=2.55cm]{resources/Fig_Intro/intro_2_1}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.065\textwidth}
            \includegraphics[height=2.55cm]{resources/Fig_Intro/intro_2_2}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.085\textwidth}
            \includegraphics[height=2.55cm]{resources/Fig_Intro/intro_1_0}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.085\textwidth}
            \includegraphics[height=2.55cm]{resources/Fig_Intro/intro_1_1}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.085\textwidth}
            \includegraphics[height=2.55cm]{resources/Fig_Intro/intro_1_2}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{0.156\textwidth}
            \includegraphics[height=2.8cm]{resources/Fig_Intro/intro_0_0}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.156\textwidth}
            \includegraphics[height=2.8cm]{resources/Fig_Intro/intro_0_1}
    \end{subfigure}
  	\hfill
    \begin{subfigure}[b]{0.156\textwidth}
            \includegraphics[height=2.8cm]{resources/Fig_Intro/intro_0_2}
    \end{subfigure}
    \caption{Comparison of the classical landmark annotation (red dots) with the curve annotation (blue lines) of hands, ears and faces.}
    \label{fig:intro}
\end{figure}

Building and fitting statistical deformable models of objects is a well-studied and popular area in the intersection of computer vision and machine learning \cite{Cootes1995, Cootes2001, Matthews2004, Saragih2011, Belhumeur2011, Zhu2012, Xiong2013}. Recently, we have witnessed tremendous developments in building and fitting models of human faces and bodies using images captured in unconstrained recording environments, usually referred to as ``in-the-wild" \cite{Belhumeur2011, Cao2012, Zhu2012, Xiong2013, Asthana2013, Tzimiropoulos2014, Asthana2014}. This is attributed to:
\begin{itemize}

\item The abundance of complex visual data, spread mostly through the Internet via web services such as Youtube, Flickr and Google Images. The latter has led to the development of large databases of ``in-the-wild" images of human faces and bodies \cite{Belhumeur2011, Le2012, Zhu2012, Burgos2013}.

@@

\item Equally important is the task of manual annotation of images with regards to face and body parts and that has been undertaken by several research teams \cite{sagonas_iccv_300w_2013,charles2013domain,dantone2014body,andriluka14cvpr}.

>>>>

\begin{figure}[t!]
    \centering
    \begin{subfigure}[b]{0.09125\textwidth}
            \includegraphics[height=3.25cm]{resources/MotivativeAnnotation/MPII}
            \caption{MPII}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.1125\textwidth}
            \includegraphics[height=3.25cm]{resources/MotivativeAnnotation/FashionPose}
            \caption{Fashion}
    \end{subfigure}
  	\hfill
    \begin{subfigure}[b]{0.125\textwidth}
            \includegraphics[height=3.25cm]{resources/MotivativeAnnotation/FLIC}
            \caption{FLIC}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.125\textwidth}
            \includegraphics[height=3.25cm]{resources/MotivativeAnnotation/BBCPose}
            \caption{BBC Pose}
    \end{subfigure}
    \caption{Visualisation of inconsistent and inaccurate annotations of human pose among different datasets. \emph{Blue} dots denote the original annotations. The arrows and \emph{green} dots show the correct location at which the points should be.
    %Original annotations are shown in blue dots while better annotations shown in green dots.
    }
    \label{fig:wrong_anno}
\end{figure}
\begin{figure}[t!]
    \centering
    \begin{subfigure}[b]{0.065\textwidth}
            \includegraphics[height=2.55cm]{resources/Fig_Intro/intro_2_0}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.065\textwidth}
            \includegraphics[height=2.55cm]{resources/Fig_Intro/intro_2_1}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.065\textwidth}
            \includegraphics[height=2.55cm]{resources/Fig_Intro/intro_2_2}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.085\textwidth}
            \includegraphics[height=2.55cm]{resources/Fig_Intro/intro_1_0}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.085\textwidth}
            \includegraphics[height=2.55cm]{resources/Fig_Intro/intro_1_1}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.085\textwidth}
            \includegraphics[height=2.55cm]{resources/Fig_Intro/intro_1_2}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{0.156\textwidth}
            \includegraphics[height=2.8cm]{resources/Fig_Intro/intro_0_0}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.156\textwidth}
            \includegraphics[height=2.8cm]{resources/Fig_Intro/intro_0_1}
    \end{subfigure}
  	\hfill
    \begin{subfigure}[b]{0.156\textwidth}
            \includegraphics[height=2.8cm]{resources/Fig_Intro/intro_0_2}
    \end{subfigure}
    \caption{Comparison of the standard landmark annotation (\emph{red} dots) with the curve annotation (\emph{blue} lines) on hands, ears and faces.}
    \label{fig:intro}
\end{figure}

Building and fitting Statistical Deformable Models (SDMs) of various object classes is a well-studied and popular area in the intersection of computer vision and machine learning \cite{Cootes1995, Cootes2001, Matthews2004, Saragih2011, Belhumeur2011, Zhu2012, Xiong2013}. Recently, we have witnessed tremendous developments in building and fitting SDMs of human faces and bodies using images that are captured under unconstrained conditions, usually referred to as ``in-the-wild" \cite{Belhumeur2011, Cao2012, Zhu2012, Xiong2013, Asthana2013, Tzimiropoulos2014, Asthana2014}. This is attributed to:
\begin{itemize}
\item The abundance of complex visual data, spread mostly through the internet via web services such as Youtube, Flickr and Google Images. The latter has led to the development of large ``in-the-wild" databases of human faces and bodies \cite{Belhumeur2011, Le2012, Zhu2012, Burgos2013}.

@@

\item Equally important is the task of manual annotation of images with regards to face and body parts and that has been undertaken by several research teams \cite{sagonas_iccv_300w_2013,charles2013domain,dantone2014body,andriluka14cvpr}.
\end{itemize}
